Using Heavy-Tailed Self-Regularization Theory to Characterize Correlations in and Perform Diagnostics on State-of-the-art Overparameterized Models

### 2021-02-18 submission/TOPML_Workshop/paper.tex
added figure 2

>>>>

\begin{figure}[t!] 
    \centering
    \subfigure[Sharpness]{
       \includegraphics[width=3.5cm]{img/Sharpness_task2.png}
    }
    \subfigure[SVDSmoothing]{
       \includegraphics[width=3.5cm]{img/SVDSmoothing_task2.png}
    }
    \caption{Applying the Sharpness (Shape) and SVDSMoothing (Scale) transforms to pretrained DNNs, we can correct for overparemeterization and predict test accuracies remarkably well by evaluating the training accuracy on the transformed models}
    \label{fig:smoothing}
\end{figure}
